A survey of HTTP caching options on the open Web

### 2015-01-15 sanity/paper1.tex
remove todo
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@987 43ef1190-90fd-4dd7-a769-d0121f02b80e
comment on the small number of resources
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@988 43ef1190-90fd-4dd7-a769-d0121f02b80e

\title{A survey of HTTP caching options on the open Web}
\author{Kjetil Kjernsmo\inst{1}}
\institute{Department of Informatics,
Postboks 1080 Blindern,
N-0316 Oslo, Norway \email{kjetil@kjernsmo.net}}

@@

Linked Data Fragments \cite{ldf1} claims to take advantage of caching
and contrasts this with the unavailability of SPARQL query caches, and
claims this is an architectural problem.

@@

For each unique \httph{Server} header, we found the ones where
\emph{all} responses had a freshness time or a promising feature. For
the former, this amounted to 22 servers, see 
Table~\ref{tab:servers}. 70 servers always responded with promising
features. As we can see, apart from well-known Virtuoso and
Callimachus servers, as well as the Perl modules RDF::LinkedData and
RDF::Endpoint, which is partly developed by and runs on a server
operated by this author, most headers tells very little about the
RDF-specific parts of the underlying server implementation. A quick
inspection of all \httph{Server} headers confirmed that few reveal any
further detail.

% latex table generated in R 2.15.1 by xtable 1.5-6 package
% Mon Jan  5 11:27:35 2015
\begin{table}[ht]
  \caption{\httph{Server} headers for hosts that enabled a freshness
    lifetime to be computed for all requests.}\label{tab:servers}
\begin{center}
\begin{tabular}{rl}
  \hline
1 & DFE/largefile \\ 
  2 & git\_frontend \\ 
  3 & nginx/1.3.9 \\ 
  4 & thin 1.6.0 codename Greek Yogurt \\ 
  5 & Oracle-Application-Server-10g/10.1.3.4.0 Oracle-HTTP-Server [\ldots]\\
  6 & Oracle-Application-Server-10g/10.1.3.4.0 Oracle-HTTP-Server [\ldots]\\
  7 & TwistedWeb/8.2.0 \\ 
  8 & RDF::Endpoint/0.07 \\ 
  9 & Jetty(6.1.26) \\ 
  10 & nginx/1.6.1 \\ 
  11 & Jigsaw/2.3.0-beta3 \\ 
  12 & Apache/2.2.9 (Win32) PHP/5.2.6 \\ 
  13 & Apache/2.4.10 (Unix) mod\_fcgid/2.3.9 \\ 
  14 &  \\ 
  15 & GFE/2.0 \\ 
  16 & RDF::LinkedData/0.70 \\ 
  17 & Apache/2.2.17 (Unix) mod\_wsgi/3.3 Python/2.6.6 \\ 
  18 & Virtuoso/07.10.3211 (Linux) i686-generic-linux-glibc212-64  VDB \\ 
  19 & Apache/2.2.24 (Unix) mod\_ssl/2.2.24 OpenSSL/0.9.8y \\ 
  20 & Apache/2.2.22 (Fedora) \\ 
  21 & INSEE \\ 
  22 & GitHub.com \\ 
   \hline
\end{tabular}
\end{center}
\end{table}

@@

We obtained a successful response from a total 2965 information
resources, either with SPARQL results or RDF data. A successful
response is rather strictly defined, not only must there be a
successful HTTP response after redirects are resolved, the response
must also return a valid RDF media type (unless it is a SPARQL result)
and the response must parse into an RDF model.

@@

In this work, we have only explored the cases where the server is
cooperative, in the sense that message data or metadata provides at
least a hint of a resource's cacheability. We also noted that the
majority of the Semantic Web is unhelpful. Therefore, an interesting
direction is to learn the change frequency of resources to use in a
heuristic freshness lifetime estimation. However, such work should
operate within the loose constraints of RFC7234, Section~4.2.2, and
should find it niche when the other techniques described in this paper
are unavailable. Once this is done, the correctness of caching headers
should be assessed, possibly using contingency tables.

@@

\subsection{Recommendations}\todo{write}

>>>>

\title{A survey of HTTP caching options on the open Web}
\author{Kjetil Kjernsmo}
\institute{Department of Informatics,
Postboks 1080 Blindern,
N-0316 Oslo, Norway \email{kjetil@kjernsmo.net}}

@@

Linked Data Fragments \cite{ldf1} is said to take advantage of caching
and contrasts this with the unavailability of SPARQL query caches, and
it is claimed that this is an architectural problem.

@@

For each unique \httph{Server} header, we found the ones where
\emph{all} responses had a freshness time or a promising feature. For
the former, this amounted to 22 servers, see 
Table~\ref{tab:servers}. 70 servers always responded with promising
features. As we can see, apart from well-known Virtuoso and
Callimachus servers, as well as the Perl modules RDF::LinkedData and
RDF::Endpoint, which is partly developed by and runs on a server
operated by this author, most headers tell very little about the
RDF-specific parts of the underlying server implementation. A quick
inspection of all \httph{Server} headers confirmed that few reveal any
further detail.

% latex table generated in R 2.15.1 by xtable 1.5-6 package
% Mon Jan  5 11:27:35 2015
\begin{table}[hb]
  \caption{\httph{Server} headers for hosts that enabled a freshness
    lifetime to be computed for all requests.}\label{tab:servers}
\begin{center}
\begin{tabular}{rl}
  \hline
1 & DFE/largefile \\ 
  2 & git\_frontend \\ 
  3 & nginx/1.3.9 \\ 
  4 & thin 1.6.0 codename Greek Yogurt \\ 
  5 & Oracle-Application-Server-10g/10.1.3.4.0 Oracle-HTTP-Server [\ldots]\\
  6 & Oracle-Application-Server-10g/10.1.3.4.0 Oracle-HTTP-Server [\ldots]\\
  7 & TwistedWeb/8.2.0 \\ 
  8 & RDF::Endpoint/0.07 \\ 
  9 & Jetty(6.1.26) \\ 
  10 & nginx/1.6.1 \\ 
  11 & Jigsaw/2.3.0-beta3 \\ 
  12 & Apache/2.2.9 (Win32) PHP/5.2.6 \\ 
  13 & Apache/2.4.10 (Unix) mod\_fcgid/2.3.9 \\ 
  14 &  \\ 
  15 & GFE/2.0 \\ 
  16 & RDF::LinkedData/0.70 \\ 
  17 & Apache/2.2.17 (Unix) mod\_wsgi/3.3 Python/2.6.6 \\ 
  18 & Virtuoso/07.10.3211 (Linux) i686-generic-linux-glibc212-64  VDB \\ 
  19 & Apache/2.2.24 (Unix) mod\_ssl/2.2.24 OpenSSL/0.9.8y \\ 
  20 & Apache/2.2.22 (Fedora) \\ 
  21 & INSEE \\ 
  22 & GitHub.com \\ 
   \hline
\end{tabular}
\end{center}
\end{table}

@@

We obtained a successful response from a total 2965 information
resources, either with SPARQL results or RDF data. A successful
response is rather strictly defined, not only must there be a
successful HTTP response after redirects are resolved, the response
must also return a valid RDF media type (unless it is a SPARQL result)
and the response must parse into an RDF model. We have given priority
to survey many hosts since configuration usually doesn't differ much
across a host, especially since it also captures different types of
resources. It is therefore acceptable that the number of resources is
relatively small.

@@

In this work, we have only explored the cases where the server is
cooperative, in the sense that message data or metadata provides at
least a hint of a resource's cacheability. We also noted that the
majority of the Semantic Web is unhelpful. Therefore, an interesting
direction is to learn the change frequency of resources to use in a
heuristic freshness lifetime estimation. However, such work should
operate within the loose constraints of RFC7234, Section~4.2.2, and
should find it niche when the other techniques described in this paper
are unavailable. Once this is done, the correctness of caching headers
should be assessed, possibly using contigency tables.

@@

\subsection{Recommendations}
